Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)

### 2014-03-01 authorinstr_2.tex
Laatste aanpassingen voor vandaag. Vakcode aangepast, werktitel toegevoegd en een klein stukje geschreven

\title{Seminarium IN3130\\ Title goes here}
\author{A. Hambenne  \and
    O. Maas \and
    R. Oosterloo}
\date{}

@@

After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by \cite{eventident} to identify an event cluster. 
\begin{itemize}
  \item Temporal: TODO
  \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
  \item Twitter-centric: TODO
\end{itemize}
With this list of features two event-classifiers are trained using two different techniques. The first classifier is trained using the "WEKA tookit"(TODO), in the second classifier the  Naive-Bayes technique is used. According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters. 
\\\\
\textbf{Aligning Tweets with an Event} \\
On average thousands of tweets are sent using Twitter(bron) every minute. One of the main challenges in Event Identification is the alignment of tweets with their respective event. \cite{eventalign} tries to create an automated mapping solution for this problem using semantics.

\section{Conclusion}

>>>>

\title{Seminarium TI 3700\\ Data Analysis on Twitter: An Overview (working title)}
\author{A. Hambenne  \and
    O. Maas \and
    R. Oosterloo}
\date{}

@@

After the clustering a number of features is used to distinguish between event and non-event clusters. The following features are used by \cite{eventident} to identify an event cluster. 
\begin{itemize}
  \item Temporal: TODO
  \item Social: The interactions between users(e.g. retweets, replies \& mentions) during events could differ from other activities. 
  \item Topical: Tweets about events tend to center more around one central topic. Furthermore messages in event clusters are more likely to share one or more event-specific key-terms.  
  \item Twitter-centric: TODO
\end{itemize}
With this list of features two event-classifiers are trained using two different techniques. The first classifier is trained using the "WEKA tookit"(TODO), in the second classifier the  Naive-Bayes technique is used. According to \cite{eventident} the first classifier outperforms the second classifier in the separation of event and non-event clusters. 
\\\\
\textbf{Aligning Tweets with an Event} \\
On average thousands of tweets are sent every minute using Twitter(bron) . One of the main challenges in Event Identification is the alignment of tweets with their respective event. \cite{eventalign} tries to create an automated mapping solution for this problem using semantics.  
Twitter exposes the data using different formats such as JSON \& XML. To make this data more machine readable \cite{eventalign} enrich the data with sematics, after this process the data can then  be used as linked data which is more machine readable. The full enrichment process is described in section 2 of \cite{eventalign}. 
TODO
\section{Conclusion}
